---
title: "ARLClustering - Testing Facebook L1 Organization dataset"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ARLClustering - Testing Facebook L1 Organization dataset}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(arlclustering)
#library(igraph)
```

## Dataset description
The Facebook L1 organization social network dataset is a gml file, containing 5793 nodes and 45266 edges.


## Loading network dataset
- Graph Label    : Facebook L1 Organization
- Total Nodes    : 5793
- Total Edges    : 45266
- Average Degree : 15.62783
```{r}
# Start the timer
t1 <- system.time({
  dataset_path <- system.file("extdata", "Facebook_Org_L1.gml", package = "arlclustering")
  if (dataset_path == "") {
    stop("Facebook_Org_L1.gml file not found")
  }
  
  g <- arlc_get_network_dataset(dataset_path, "Facebook L1 Organization")
  g$graphLabel
  g$totalNodes
  g$totalEdges
  g$averageDegree
})

# Display the total processing time
message("Graph loading Processing Time: ", t1["elapsed"], " seconds\n")
```

## Generate Transactions

Next, we generate transactions from the graph, with a total rows of 3541.

```{r}
# Start the timer
t2 <- system.time({
  transactions <- arlc_gen_transactions(g$graph)
  transactions
})

# Display the total processing time
message("Transaction dataset Processing Time: ", t2["elapsed"], " seconds\n")
```

## Get Apriori Thresholds

We obtain the apriori thresholds for the generated transactions. The following are the thresholds for the apriori execution:
- The Minimum Support    : 0.002
- The Minimum Confidence : 0.5
- The Lift               : 442.625
- The Gross Rules length : 97825
- The selection Ratio    : 28

```{r}
# Start the timer
t3 <- system.time({
  params <- arlc_get_apriori_thresholds(transactions,
                                        supportRange = seq(0.002, 0.003, by = 0.001),
                                        Conf = 0.5)
  params$minSupp
  params$minConf
  params$bestLift
  params$lenRules
  params$ratio
})

# Display the total processing time
message("Graph loading Processing Time: ", t3["elapsed"], " seconds\n")
```

## Generate Gross Rules

We use the obtained parameters to generate gross rules, where we obtain 97858 rules.

```{r}
# Start the timer
t4 <- system.time({
  minLenRules <- 1
  maxLenRules <- params$lenRules
  if (!is.finite(maxLenRules) || maxLenRules > 5*length(transactions)) {
    maxLenRules <- 5*length(transactions)
  }
  
  grossRules <- arlc_gen_gross_rules(transactions,
                                     minSupp = params$minSupp,
                                     minConf = params$minConf,
                                     minLenRules = minLenRules+1,
                                     maxLenRules = maxLenRules)
  grossRules$TotalRulesWithLengthFilter
})
# Display the total number of clusters and the total processing time
message("Gross rules generation Time: ", t4["elapsed"], " seconds\n")
```

## Filter Significant and Non-Redundant Rules

We filter out redundant rules from the generated gross rules. Next, we filter out non-significant rules from the non-redundant rules, and we obtain the 18907 rule items.

```{r}
t5 <- system.time({
  NonRedRules <- arlc_get_NonR_rules(grossRules$GrossRules)
  NonRSigRules <- arlc_get_significant_rules(transactions,
                                             NonRedRules$FiltredRules)
  NonRSigRules$TotFiltredRules
})
# Display the total number of clusters and the total processing time
message("\nClearing rules Processing Time: ", t5["elapsed"], " seconds\n")
```

## Clean and genarate final Rules

We clean the final set of rules to prepare for clustering. Then, we generate clusters based on the cleaned rules. The total identified clusters is 190 clusters.

```{r}
t6 <- system.time({
  cleanedRules <- arlc_clean_final_rules(NonRSigRules$FiltredRules)
  clusters <- arlc_generate_clusters(cleanedRules)
  clusters$TotClusters
})
# Display the total number of clusters and the total processing time
message("Cleaning final rules Processing Time: ", t6["elapsed"], " seconds\n")

message("The total comsumed time is:",t1["elapsed"]+ t2["elapsed"]+t3["elapsed"]+t4["elapsed"]+t5["elapsed"]+t6["elapsed"], "seconds\n")
```

## Plot Clusters

Finally, we visualize the identified clusters.

```{r}
arlc_clusters_plot(g$graph,
                   g$graphLabel,
                   clusters$Clusters)

```


